Pre-trained encoders for dialogue: The case of laughter

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
add preprocessing section

\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.

@@

\paragraph{}
Let us turn now to describing the neural network architectures that we used.

@@

The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.

@@

Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought. Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix. However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
\begin{table}
      \small
  \centering
  \begin{tabularx}{\linewidth}{llL}
    \toprule
    Speaker & DA & Utterance \\ \midrule
        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
    B   & sd	&  Um, as far as spare time, they talked about, \\
    B	& \% & I don't, + I think, \\
    B	& qh & who has any spare time \texttt{<laughter>}? \\
    A	& x & \texttt{<laughter>}.\\
             \bottomrule
  \end{tabularx}
  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
  \label{table:example-qh}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{@{}llcc@{}}
    \toprule
    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
  \end{tabular}
  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
  \label{table:laughter-group-acc}
\end{table}

@@

%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training
\paragraph{}
Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.

>>>>

@@

@@

@@

Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought. Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix. However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
\begin{table}
      \small
  \centering
  \begin{tabularx}{\linewidth}{llL}
    \toprule
    Speaker & DA & Utterance \\ \midrule
        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
    B   & sd	&  Um, as far as spare time, they talked about, \\
    B	& \% & I don't, + I think, \\
    B	& qh & who has any spare time \texttt{<laughter>}? \\
    A	& x & \texttt{<laughter>}.\\
             \bottomrule
  \end{tabularx}
  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
  \label{table:example-qh}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{@{}llcc@{}}
    \toprule
    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
  \end{tabular}
  \caption{Comparison of models depending on using laughter on the training phase. }
  \label{table:laughter-group-acc}
\end{table}

@@

%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training
